---
title: ''
output:
  html_document: default
  html_notebook: default
  pdf_document: default
  word_document: default
---



```{r,echo = FALSE, message = FALSE}
library(readr)
hotel_df2 <- read_csv("~/Documents/dsR/data/hotel_df2.csv")
hotel_df2 = hotel_df2[,-1]

hotel_df <- read_csv("~/Documents/dsR/data/hotel_df.csv")
hotel_df = hotel_df[, -1]

require(dplyr)
new_df = inner_join(hotel_df,hotel_df2,by = "name")

```

```{r,echo = FALSE, message = FALSE}




district = NULL 
for(i in c(1:569)){
  end = regexpr("區",new_df[i,c("address")])
  
  a = substr(new_df[i,7],end - 2, end)
  
  district =rbind( district, a)
  
  }
new_df = cbind(new_df,district)
as.character(new_df[1,7])

MRT = NULL
MRT_dist = NULL
for(i in c(1:569)){
  for(j in c(1:6)){
    if(regexpr("捷運",new_df[i, 31 + j])>0){
      r = new_df[i, 38 + j]
      start = regexpr("運",new_df[i,31 + j])
      end  = regexpr("站", new_df[i,31 + j])
      mrt = substr(new_df[i,31 + j], start+1, end-1)
      
      MRT = rbind(MRT, mrt)
      MRT_dist = rbind(MRT_dist, r)
      break
    }
    if(j == 6){
      MRT = rbind(MRT, NA)
      MRT_dist = rbind(MRT_dist, NA)
    }
  }
}
```



```{r,echo = FALSE, message = FALSE}




new_df = cbind(new_df,MRT,MRT_dist)
new_df$wifi_level = as.numeric(new_df$wifi_level)
new_df$facility_level = as.numeric(new_df$facility_level)

total_pricetwo2 = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star),new_df_starExist )

#summary(total_pricetwo1)
new_df$facility_level = as.numeric(new_df$facility_level)
new_df$wifi_level = as.numeric(new_df$wifi_level)


```

#hedonic pricing model
```{r,echo = FALSE, message = FALSE}

total_pricetwo0_log = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist,new_df_starExist )
total_pricetwo4_log =  lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+as.factor(district),new_df)
a = summary(total_pricetwo4_log)
a$coefficients


new_df_one$lprice_two = log(new_df_one$price_two)
singleroom_pricetwo0_log  = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist
                           ,new_df_one )


singleroom_pricetwo1_log  = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level,new_df_one )

singleroom_pricetwo2_log  = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star),new_df_one )

singleroom_pricetwo3_log  = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+as.factor(district),new_df_one )

a = summary(singleroom_pricetwo3_log)
a$coefficients[, 2]


 
     
   
summary(total_pricetwo3_log)


             
             


   
  



  
  
 
   


```
```{r}

total_pricetwo1_log = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+  clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level,new_df_starExist )


total_pricetwo2_log = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+  clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star),new_df_starExist )

total_pricetwo3_log = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+  clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+as.factor(district),new_df_starExist )


```
```{r}
total_pricetwo0 = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist,new_df_starExist )
total_pricetwo1 = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+  I(clean_level^2)+I(clean_level^3)+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level,new_df_starExist )

total_pricetwo3 = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district),new_df_starExist )
a = summary(total_pricetwo1)
coef(a)[, 2]
a
   
total_pricetwo4 =  lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+as.factor(district),new_df)
a = summary(singleroom_pricetwo3)
a
length(singleroom_pricetwo3$fitted.values)
total_pricetwo4$coefficients  
coef(a)[, 2]

 
 summary(total_pricetwo3)       

ggplot(new_df_starExist, aes(x = cp_level, y = price_two))+geom_smooth()
#summary(total_pricetwo2)
head(new_df)
```
#correlation matrix
```{r}
library(Hmisc)
library(polycor)
c("minibar","gym", "self_breakf",  "flatTV", "spa", "parking", "restaurant", "bathtub", "securityBox" , "nightmarket","clean_level", "comfort_level", "facility_level", "location_level", "service_level", "cp_level", "wifi_level")
x = test[, c("minibar","gym", "self_breakf",  "flatTV", "spa", "parking", "restaurant", "bathtub", "securityBox" , "nightmarket","clean_level", "comfort_level", "facility_level", "location_level", "service_level", "cp_level", "wifi_level", "MRT_dist")]
rcorr(x, type="pearson")
cor(x, x)
polychor(x) 
test = filter(new_df_starExist, is.na(clean_level) == FALSE & is.na(comfort_level) == FALSE& is.na(facility_level) == FALSE& is.na(location_level) == FALSE& is.na(service_level) == FALSE& is.na(cp_level) == FALSE& is.na(wifi_level) == FALSE& is.na(MRT_dist) == FALSE)
class(new_df_starExist$MRT_dist)
new_df_starExist$clean_level = as.integer(new_df_starExist$clean_level)
new_df_starExist$gym = as.integer(new_df_starExist$gym)
new_df_starExist$comfort_level = as.integer(new_df_starExist$comfort_level)
new_df_starExist$facility_level = as.integer(new_df_starExist$facility_level)
new_df_starExist$location_level =as.integer(new_df_starExist$location_level)
new_df_starExist$service_level =as.integer(new_df_starExist$service_level)
new_df_starExist$cp_level = as.integer(new_df_starExist$cp_level)
new_df_starExist$wifi_level = as.integer(new_df_starExist$wifi_level)
```

#first table
```{r,echo = FALSE, message = FALSE}

t = lm(price_two~cp_level,new_df)
require(memisc)
mt = mtable( 'model' = t,summary.stats = c('R-squared','F','p','N'))

require(pander)
library(sjPlot)
sjt.lm( singleroom_pricetwo3_log, depvar.labels = c("model0","model1", "model2", "model3"), file="output.html",p.numeric = FALSE)# You have to save the table in html format.
htmltools::includeHTML("output.html")

stock = dyn$lm(y1 ~ x1 + lag(x2, -1) + x2 + x3 +x4)
stock_matrix <- matrix(summary(stock)$coef, ncol = 4L)
 try = matrix(summary(total_pricetwo0_log)$coef, ncol = 4L)
rownames(stock_matrix) <- c("Intercept", "$x_{1,t}$", "$x_{2,t-1}$", "$x_2$", "$x_3$", "$x_4$")

print(xtable(try), sanitize.text.function = identity)
?xtable
newobject<-xtable(try)
print.xtable(newobject, type="html", file="filename.html")
xtable(linR)
myregtables <- cbind(xtable(summary(quantreg25)), xtable(summary(quantreg50)))
myregtables
texreg(list(top25_rq,top50_rq, top75_rq ), se = "iid")
texreg(list(singleroom_pricetwo0_log, singleroom_pricetwo1_log, singleroom_pricetwo2_log), se = "iid")
single
texreg(total_pricetwo3_log, se = "iid")
singleroom_pricetwo3_log
quantreg25
summary(total_pricetwo4_log)
```
```{r}
##first table bootstrap

#{
# Bootstrap 95% CI for R-Squared
library(boot)
# function to obtain R-Squared from the data 
rsq <- function(formula, data, indices) {
  d <- data[indices,] # allows boot to select sample 
  fit <- lm(formula, data=d)
  return(summary(fit)$r.square)
} 
# bootstrapping with 1000 replications 
results <- boot(data=new_df, statistic=rsq, 
  	R=1000, formula=price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+MRT_dist+location_level+wifi_level)

# view results
results 
plot(results)

# get 95% confidence interval 
boot.ci(results, type="bca")

```
```{r}
set.seed(3244)
bstar = NULL # Rows of bstar will be bootstrap vectors of regression coefficients.
n = length(new_df$price_two); 
B = 1000

for(draw in 1:B) {
# Randomly sample from the rows of kars, with replacement
Dstar = new_df[sample(1:n,size=n,replace=T),]
model = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+MRT_dist+location_level+wifi_level+as.factor(star)+factor(district), data=new_df) 

bstar = rbind(bstar,coef(model) )
} # Next draw
bstar[1:5,]
Vb = var(bstar)

betahat = total_pricetwo3$coefficients
se = sqrt(diag(Vb));
Z = betahat/se
rbind(betahat,se,Z)



```

```{r,echo = FALSE, message = FALSE}
require(lmtest)
require(plm)
coeftest(total_pricetwo1, vcov = vcovHC(total_pricetwo1, "HC1")) 



```
```{r,echo = FALSE, message = FALSE}

coeftest(total_pricetwo2, vcov = vcovHC(total_pricetwo2, "HC1")) 

```
```{r,echo = FALSE, message = FALSE}


#anova(total_pricetwo1, total_pricetwo2)

```


#hedonic price model(price one)
```{r,echo = FALSE, message = FALSE}
require(dplyr)
#new_df_one  ==  those hotels that the price of the single room is nonNA
new_df_one = filter(new_df_starExist,is.na(price_one) == F )

head(new_df_one)
singleroom_pricetwo0  = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist,new_df_one )
#summary(singleroom_pricetwo1)
singleroom_pricetwo2$coefficients
 a = summary(singleroom_pricetwo2)
coef(a)[, 2]
table(new_df_one$star)
nrow(new_df_one)
length(new_df$price_four[which(is.na(new_df$price_four))])
which(is.na(new_df$price_one))

new_df_starExist$price_four[]
levels(as.factor(new_df_one$star))
 
ggplot(new_df_one)+stat_qq(aes(sample = price_two, colour = factor(star)))

singleroom_pricetwo3$coefficients
  a = summary(singleroom_pricetwo3)
a
  coef(a)[, 2]
table(new_df_one$star)
  
 

    
```

```{r,echo = FALSE, message = FALSE}
singleroom_pricetwo1  = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level,new_df_one )
#summary(singleroom_pricetwo2)
singleroom_pricetwo2 = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star), new_df_one)


singleroom_pricetwo3 = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district), new_df_one)
```
```{r,echo = FALSE, message = FALSE}
#anova(singleroom_pricetwo1, singleroom_pricetwo2)

```
```{r,echo = FALSE, message = FALSE}
singleroom_priceone1  = lm(price_one~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+MRT_dist,new_df_one )

##summary(a1_one_one)
```
```{r,echo = FALSE, message = FALSE}
singleroom_priceone2  = lm(price_one~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+MRT_dist+as.factor(star),new_df_one )
##summary(a_one_one)
singleroom_priceone3 = lm(price_one~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+MRT_dist+as.factor(star)+factor(district), new_df_one)
```
```{r,echo = FALSE, message = FALSE}
#anova(a_one, a1_one)
#head(new_df)

```
#for log price one 
```{r}



```

#second table
```{r,echo = FALSE, message = FALSE}
#a_one,singleroom_pricetwo3
#a1_one ,"model3"
sjt.lm( singleroom_pricetwo0,singleroom_pricetwo1,singleroom_pricetwo2,depvar.labels = c("model0","model 1", "model2"), file="output.html",p.numeric = FALSE)# You have to save the table in html format.
htmltools::includeHTML("output.html")
#sjt.lm(top75_ols,  file="output.html",p.numeric = FALSE)

```
#third table
```{r,echo = FALSE, message = FALSE}
sjt.lm( singleroom_priceone1, singleroom_priceone2,depvar.labels = c("model 1", "model 2"), file="output.html",p.numeric = FALSE)# You have to save the table in html format.
htmltools::includeHTML("output.html")


```
#bootstrap  error term isnt normal distribution or under small sample

```{r,echo = FALSE, message = FALSE}
require(ggplot2)

```
#another regression for individual scoring

```{r,echo = FALSE, message = FALSE}
command_df <- read_csv("~/Documents/dsR/code/command_df.csv")
command_df = command_df[, -1]
attach(command_df)
#head(command_df)

#test = substr("單人","獨行旅客", command_df$type )
#table(type = command_df$type, goal = command_df$goal)
#names(command_df)
#clean = filter(command_df, type == c("獨行旅客","夫婦/情侶","帶青少年同行的家庭","朋友團體", "攜帶幼童的家庭", ))
#table(clean$type)
#head(clean)
#table(clean$goal)


#anova(ols_command, ols_command_nogoal)

command_df_re = command_df[ which(!is.na(command_df$night)), ]
command_df_re = command_df_re[which(!is.na(command_df_re$goal)),]
ols_command = lm(grade~factor(goal)+factor(night), command_df_re)
a = summary(ols_command)
length(ols_command$fitted.values)
coef(a)[, 2]
ols_command$coefficients
a


 

              

texreg(grade_ols)


```
```{r}
require(dplyr)
haveNightmarket = filter(new_df_starExist, nightmarket == 1)
require(ggplot2)
ggplot(haveNightmarket, aes(x = star))+stat_qq(aes(sample = price_two, colour = factor(star)))+geom_boxplot(aes(y = price_two, colour = factor(star)))+labs(title = "table 1", subtitle = "hotel neaby the nightmarket" )
#+labs(title="figure 3",subtitle="price for double room under different ratings")
ggplot(haveNightmarket, aes(x = star))+geom_histogram(aes(colour = factor(star)))+labs(title = "table 1", subtitle = "hotel neaby the nightmarket" )
```
```{r}

ggplot(new_df_starExist, aes(x = star))+stat_qq(aes(sample = price_two, colour = factor(star)))+geom_boxplot(aes(y = price_two, colour = factor(star)))+labs(title = "table 2", subtitle = "all hotels")
ggplot(new_df_starExist, aes(x = star))+stat_qq(aes(sample = price_two))
```


```{r}
ggplot(haveNightmarket)+stat_qq(aes(sample = price_two, colour = factor(star)))+labs(title="figure 3",subtitle="price for double room under different ratings")
```

```{r}


ols_command_nogoal = lm(grade~factor(night), command_df_re)
ols_command_su = summary(ols_command)
summary(ols_command_nogoal)
anova(ols_command_nogoal, ols_command)
length(ols_command$fitted.values)
command_df_re$fittedGrade = ols_command$fitted.values
grade_ave0 = command_df_re%>%group_by(hotel)%>%summarise(ave = mean(fittedGrade))
grade_ave0

combine_ave_df0 = inner_join(hotel_df, grade_ave0, by = "hotel")
combine_ave_df0$clean_level = as.numeric(combine_ave_df0$clean_level)
combine_ave_df0$comfort_level = as.numeric(combine_ave_df0$comfort_level)
combine_ave_df0$facility_level = as.numeric(combine_ave_df0$facility_level)
combine_ave_df0$location_level = as.numeric(combine_ave_df0$location_level)
combine_ave_df0$service_level = as.numeric(combine_ave_df0$service_level)
combine_ave_df0$cp_level = as.numeric(combine_ave_df0$cp_level)
combine_ave_df0$wifi_level = as.numeric(combine_ave_df0$wifi_level)

overall_level = combine_ave_df0%>%group_by(hotel)%>%summarise(overall_level =( clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level)/7)

grade_ols = lm(overall_level~ave, combine_ave_df)
length(grade_ols$fitted.values)

summary(grade_ols)
combine_ave_df

new_df_starExist$lprice_two = log(new_df_starExist$price_two)
lprice_lm = lm(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level
               , new_df_starExist)

a = summary(lprice_lm)
a$coefficients
vif(lprice_lm)
```
```{r}

grade_ave = command_df%>%group_by(hotel)%>%summarise(ave = mean(grade))
#grade_ave


hotel_df$hotel = rep(1:594)

combine_ave_df = inner_join(hotel_df, grade_ave, by = "hotel")

combine_ave_df$clean_level = as.numeric(combine_ave_df$clean_level)
combine_ave_df$comfort_level = as.numeric(combine_ave_df$comfort_level)
combine_ave_df$facility_level = as.numeric(combine_ave_df$facility_level)
combine_ave_df$location_level = as.numeric(combine_ave_df$location_level)
combine_ave_df$service_level = as.numeric(combine_ave_df$service_level)
combine_ave_df$cp_level = as.numeric(combine_ave_df$cp_level)
combine_ave_df$wifi_level = as.numeric(combine_ave_df$wifi_level)

overall_level = combine_ave_df%>%group_by(hotel)%>%summarise(overall_level =( clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level)/7)
combine_ave_df = inner_join(combine_ave_df, overall_level, by = "hotel")
#wifi_level+clean_level+comfort_level+facility_level+location_level+service_level+
grade_ols = lm(ave~overall_level, combine_ave_df)#???

summary(grade_ols)
#summary(grade_ols)
```
```{r}
grade_ols2 = lm(ave~clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level, combine_ave_df)
summary(grade_ols2)
```

```{r}
require(ggplot2)

ggplot(data = new_df, aes(x = star, y = price_two))+geom_jitter()+geom_smooth(stat = "smooth")

```
```{r}
require(plotly)
#ggplot(data = new_df, aes(x = district,y = price_two ))+geom_jitter()+geom_boxplot()

p <- plot_ly(new_df, y = ~price_two, color = ~district, type = "box")
p
# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started

```
```{r}

plot_ly(new_df, x =~star, y =~ price_two, color = ~star, size = ~star, text = ~paste("star ", star))

```

```{r}
rep(1:3)
new_df$num = rep(1:nrow(new_df))
  
ggplot(data = new_df, aes(x = num, y = price_two))+geom_jitter()+geom_boxplot()
plot_ly(new_df, y = ~price_two,type = "box", boxpoints = "all", jitter = 0.3,pointpos = -1.8)
quantile(new_df$price_two, na.rm = TRUE)
```
```{R}
star45 = new_df%>%filter(star == c(4,5))
quantile(star45$price_two, na.rm = TRUE)

ggplot(new_df)+stat_qq(aes(sample = price_two, colour = factor(star)))+labs(title="figure 3",subtitle="price for double room under different ratings")
ggplot(new_df)+stat_qq(aes(sample = price_one, colour = factor(star)))+labs(title="figure 4",subtitle="price for single room under different ratings")
```
```{r}
ggplot(new_df)+stat_qq(aes(sample = price_one))+labs(title="figure 1",subtitle="price for single room")
ggplot(new_df)+stat_qq(aes(sample = price_two))+labs(title="figure 1",subtitle="price for double room")

ggplot(new_df)+geom_density(aes(x = price_two))
quantile(new_df$price_two, na.rm = TRUE)
require(dplyr)
top75 = filter(new_df, is.na(price_two ) == FALSE) %>% filter(price_two >= 2680)

```

#top75 ols vs rq
```{r}

top75_ols = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level+as.factor(star)+factor(district),top75)
summary(top75_ols)
top5250 = filter(new_df, is.na(price_two ) == FALSE) %>% filter(price_two >= 5250)
#top5250_ols = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level+as.factor(star)+factor(district),top5250)
#summary(top5250_ols)


```

#quantile regression 25% 50% 75%
```{r}
top25_rq = rq(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district),new_df_starExist, tau=0.25, model = TRUE)

arq = summary(top25_rq, se = "ker")

arq
top50_rq = rq(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district),new_df_starExist, tau=0.50, model = TRUE)
arq50 = summary(top50_rq, se = "ker")

arq50

top75_rq = rq(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district),new_df_starExist, tau=0.75, model = TRUE)
arq75 = summary(top75_rq, se = "ker")
arq75
















```
```{r}
summary(total_pricetwo3)
```
#short quantile regression for 25, 50, 75%
```{R}
library(quantreg)
srq75 = rq(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist,new_df_starExist, tau=0.75, model = TRUE)
summary(srq75, se ="ker")


srq50 = rq(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist,new_df_starExist, tau=0.50, model = TRUE)
a = summary(srq50, se ="ker")


srq25 = rq(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist,new_df_starExist, tau=0.25, model = TRUE)
a =summary(srq25, se ="ker")
length(a$residuals)

confint(total_pricetwo3_log)
```
```{r}
anova(top75_rq, top25_rq)
stepAIC(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level+as.factor(star)+factor(district))

quantreg.all <- rq(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket, tau = seq(0.05, 0.95, by = 0.05), data=new_df_starExist)
quantreg.plot <- summary(quantreg.all)

```

#quantile regrssion 50%
```{r}
rq50 = rq(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level+as.factor(star)+factor(district),new_df, tau=0.50, model = TRUE)


sum_rq50 = summary(rq50, se ="ker")
length(sum_rq50$residuals)
```
```{r}



```


#tobit regression for dealing with the zero and nonzero star
```{r}
new_df_starExist = mutate(new_df, starExist = ifelse(is.na(star), 0, 1))

table(new_df_starExist$starExist)
table(new_df$star)
star_logit = glm(starExist~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level+factor(district),  family=binomial (link = "logit"), new_df_starExist)
summary(star_logit)


```
```{r}
LogitScalar <- mean(dlogis(predict(star_logit, type = "link")))
LogitScalar * coef(star_logit)
```
```{R}

is.na(new_df_starExist$star[1]) 
for(i in c(1:nrow(new_df_starExist))){
  if(is.na(new_df_starExist$star[i]) == TRUE){
    new_df_starExist$star[i] = 0
  }
}

star_re_ols = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level+as.factor(star)+as.factor(district), new_df_starExist)
summary(star_re_ols)
```
```{R}
star_re_ols2 = lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+MRT_dist+as.factor(star)+factor(district), new_df_starExist)
summary(star_re_ols2)
```
```{r}
summary(lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+MRT_dist+as.factor(star)+factor(district),new_df ))


```








```{r}
# Quantile Regression in R
# Copyright 2013 by Ani Katchova

# install.packages("quantreg")


require(quantreg)

# OLS regression
olsreg <- lm(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level,new_df )
summary(olsreg)

# Quantile regression


quantreg50 <- rq(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level,new_df , tau=0.5 )
summary(quantreg50, se = "ker")

quantreg75 <- rq(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+facility_level+service_level+MRT_dist+location_level+wifi_level , tau=0.75,new_df)
summary(quantreg75, se = "ker")

# Simultaneous quantile regression
quantreg2575 <- rq(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district),new_df_starExist, tau=c(0.25, 0.75), model = TRUE)
summary(quantreg2575,se = "ker")
table.rq(quantreg50)
# ANOVA test for coefficient differences
#anova(quantreg25, quantreg75)
?table.rq
# Plotting data
quantreg.all <- rq(price_two~factor(star), tau = c(0.25, 0.75), data=new_df)
quantreg.plot <- summary(quantreg.all)
#plot(quantreg.plot)
quantreg2575$coefficients[,2]
a = summary(quantreg25, se = "ker")
coef(a)[, 1]
a


 quantreg25 = rq(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district),new_df_starExist, tau=0.85, model = TRUE)

require(car)
vif(total_pricetwo3_log)
mean(as.numeric(new_df[,c(8:18)]))
mean(as.numeric(new_df$comfort_level))

mean(as.numeric(new_df$price_one[which(!is.na(new_df$price_one))]))
sd(as.numeric(new_df$minibar[which(!is.na(new_df$minibar))]))

```
```{r}



A <- matrix(runif(12), 4)
b <- 1:4
qr.solve(A, b) # or solve(qr(A), b)
solve(qr(A, LAPACK = TRUE), b)
data(stackloss)
rq(stack.loss~stack.x)

require(MASS)
ridgeRegression = lm.ridge(lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district), new_df_starExist, lambda = seq(0.001, .05, .001))


plot(lm.ridge(price_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district), new_df_starExist,
              lambda = seq(0,0.1,0.001)))
library(broom)
td <- tidy(ridgeRegression)
td
g <- glance(ridgeRegression)
g
require(ggplot2)
ggplot(td, aes(lambda, estimate, color = term),  family = "STKaiti") + geom_line()
ggplot(td, aes(lambda, GCV),  family = "STKaiti") + geom_line() +
    geom_vline(xintercept = g$lambdaGCV, col = "red", lty = 2)
td

require(ridge)
formula = lprice_two~minibar+gym+ self_breakf+ flatTV+spa+parking+restaurant+bathtub+securityBox+ nightmarket+MRT_dist+clean_level+comfort_level+facility_level+location_level+service_level+cp_level+wifi_level+as.factor(star)+factor(district)

linR = linearRidge(formula, new_df_starExist, lambda = "automatic", nPCs = NULL,scaling = c("corrForm", "scale", "none"))

a = summary(linR)
a
coef(linR)
mutate(new_df_starExist, coef_ols = total_pricetwo3$fitted.values)


plot(total_pricetwo3$coefficients, y = NULL)
linearRidge
#require(MASS)
#step <- stepAIC(formula, direction="both")
#stepAIC()
print(linR, digits = max(3,getOption("digits") - 3),signif.stars =getOption("show.signif.stars"))
```
```{r}
summary(lm(price_two~factor(star), new_df))



```
```{r}
 
# generate the x predictor
x <-new_df$star

# generate the y response
y <--new_df$price_two
xy <- data.frame(x=x, y=y)

# specify the maximum polynomial degree that will be explored
max.poly <- 7
 
# cretaing data.frame which will store model predictions
# that will be used for the smooth curves in Fig. 1
x.new <- seq(min(!is.na(x)), max(!is.na(x)), by=0.1)
degree <- rep(1:max.poly, each=length(x.new))
predicted <- numeric(length(x.new)*max.poly)
new.dat <- data.frame(x=rep(x.new, times=max.poly),
                      degree,
                      predicted)

Poly<- function(x, degree = 1, coefs = NULL, raw = FALSE, ...) {
       notNA<-!is.na(x)
        answer<-poly(x[notNA], degree=degree, coefs=coefs, raw=raw, ...)
        THEMATRIX<-matrix(NA, nrow=length(x), ncol=degree)
        THEMATRIX[notNA,]<-answer
        attributes(THEMATRIX)[c('degree', 'coefs', 'class')]<- attributes(answer)[c('degree', 'coefs', 'class')]
        THEMATRIX
 }


  lm( y ~ Poly(x,2) )
# fitting lm() polynomials of increasing complexity
# (up to max.degree) and storing their predictions
# in the new.dat data.frame
for(i in 1:max.poly)
{
  sub.dat <- new.dat[new.dat$degree==i,]
  new.dat[new.dat$degree==i,3] <- predict(lm(y~Poly(x, i)),
                                          newdata=data.frame(x=x.new))
}
 
# plotting the data and the fitted models
p <- ggplot()
p + geom_point(aes(x, y), xy, colour="darkgrey")
p + geom_line(aes(x, predicted,
                  colour=as.character(degree)),
                  new.dat)
p + scale_colour_discrete(name = "Degree")
p
 
# creating empty data.frame that will store
# AIC and BIC values of all of the models
AIC.BIC <- data.frame(criterion=c(rep("AIC",max.poly),
                                  rep("BIC",max.poly)),
                      value=numeric(max.poly*2),
                      degree=rep(1:max.poly, times=2))
 
# calculating AIC and BIC values of each model
for(i in 1:max.poly)
{
  AIC.BIC[i,2] <- AIC(lm(y~poly(x,i)))
  AIC.BIC[i+max.poly,2] <- BIC(lm(y~poly(x,i)))
}
 
# function that will perform the "leave one out"
# crossvalidation for a y~poly(x, degree) polynomial
crossvalidate <- function(x, y, degree)
{
  preds <- numeric(length(x))
    for(i in 1:length(x))
    {
        x.in <- x[-i]
        x.out <- x[i]
        y.in <- y[-i]
        y.out <- x[i]
        m <- lm(y.in ~ poly(x.in, degree=degree) )
        new <- data.frame(x.in = seq(-3, 3, by=0.1))
        preds[i]<- predict(m, newdata=data.frame(x.in=x.out))
    }
  # the squared error:
  return(sum((y-preds)^2))
}
 
# crossvalidating all of the polynomial models
# and storing their squared errors in
# the "a" object
a <- data.frame(cross=numeric(max.poly))
for(i in 1:max.poly)
{
  a[i,1] <- crossvalidate(x, y, degree=i)
}
 
# plotting AIC and BIC against model complexity
# (which is the polynomial degree)
AIC.plot <- qplot(degree, value, data=AIC.BIC,
                  geom="line", linetype=criterion) +
                  xlab("Polynomial degree") +
                  ylab("Criterion value") +
                  labs(title="Information theory & Bayes")+
                  geom_segment(aes(x=3, y=400,
                                   xend=3, yend=325),
                  arrow = arrow(length = unit(0.3, "cm"),
                  angle=20, type="closed")) +
                  theme(legend.position=c(0.8,0.5))
AIC.plot
 
# plotting crossvalidated squared errors agains
# model complexity
cross.plot <- qplot(1:max.poly,cross, data=a, geom=c("line"))+
                    xlab("Polynomial degree") +
                    ylab("Squared error") +
                    geom_segment(aes(x=3, y=400,
                                     xend=3, yend=200),
                    arrow = arrow(length = unit(0.3, "cm"),
                    angle=20, type="closed")) +
                    labs(title="Crossvalidation")
cross.plot


```
```{r}
head(new_df)
word = select(new_df,fir_lo, sec_lo,thir_lo,fir_hot,sec_hot,thir_hot)
word = unlist(word)

word = table(word)
word = as.data.frame(word)
as.matrix(word)
word = arrange(word,desc(Freq))

library(showtext)
require(wordcloud)
dev.new()# 新建图形设备
showtext.begin()
?showtext.begin()
quartz(family="STKaiti")
par(family = 'STHeiti')
par(family=("Heiti TC Light"))
wordcloud(word$word, word$Freq, min.freq = 10, random.order = F, ordered.colors = F,colors=brewer.pal(8, "Dark2"), family = "STKaiti")
arrange(word, desc(Freq))%>%top_n(10)
?arrange
```
```{r}
library(tm)

```




$\frac{e^{x'\beta}}{(1+e^{x'\beta})^2} $
$\sum_{i=1}^{n} X^3_i$
$\sum_{i=1}^{n}\left( \frac{X_i}{Y_i} \right)$
$a_i \ge 0~~~\forall i$
$\int_0^{2\pi} \sin x~dx$

$\mathbf{X} = \left[\begin{array}{rrr}1 & 2 & 3 \\4 & 5 & 6 \\7 & 8 & 9\end{array}\right]$

$\begin{array}{rrr}1 & 2 & 3 \\4 & 5 & 6 \\7 & 8 & 9\end{array}$

$\sqrt{b^2 - 4ac}$

$X^2_{i,j}$
